Verifying Demonstrations

### 2018-11-30 paper/protocol.tex
explains about cid comparison and why it's not in the protocol, swaps eligibility and verifiability in analysis, rephrases threshold to match with strength function, other small edits

\emph{Creation of a protest: the manifesto.}
The organizer writes a manifesto for the protest, which describes its cause.
This manifesto could take the form of any intelligible text.
The organizer will then distribute this manifesto to people through
any suitable means  (\eg on the Web, on placards, \etc).
If they agree on the cause, they will use the knowledge of the manifesto to join the protest.

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \CROCUSjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
\cref{fig:ProofFig} and \cref{ACprfAlg}).
The protester should also receive a time-correlated random value from the 
time-stamping service, \(t_s\gets \TSget\).

@@

Note that anyone who does the counting can choose the eligibility
criteria (time interval, location, number of regular or trusted
witnesses, who is considered to be a trusted witness) for their count
and as long as these are published along with the result, any one can
verify the correctness under those criteria.

>>>>

\emph{Creation of a protest: the manifesto.}
The organizer writes a manifesto for the protest, which describes its cause.
This manifesto could take the form of any intelligible text.
The organizer will then distribute this manifesto to people through
any suitable means  (\eg on the Web, on placards, \etc).
If they agree with the cause, they will use the knowledge of the
manifesto to join the protest.

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \CROCUSjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest will use the manifesto to
compute an identifier for the cause by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
from the organizer, we omit this in the protocol for readibility).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
\cref{fig:ProofFig} and \cref{ACprfAlg}).
The protester should also receive a time-correlated random value from the 
time-stamping service, \(t_s\gets \TSget\).

@@

Note that anyone who does the counting can choose the eligibility
criteria (time interval, location, number of regular or trusted
witnesses, who is considered to be a trusted witness) for their count
and as long as these are published along with the result, anyone can
verify the correctness under those criteria.

### 2018-11-30 paper/verifiability-analysis.tex
explains about cid comparison and why it's not in the protocol, swaps eligibility and verifiability in analysis, rephrases threshold to match with strength function, other small edits

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
that their participation proofs (\ie proof shares) are indeed included in the 
computed count.
All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger and 
available from a public and permanent storage (see 
\cref{fig:ProtocolOverview}).
Thus, Alice and Bob can simply check that all of their proof shares are indeed 
there and the security of individual verifiability depends on the properties of 
the ledger and storage (\(\TS\), \cref{timestamp}).
For both \cref{in-system-adversary,deanonymizing-storage-adversary} we assumed 
an honest-but-curious adversary controlling \(\TS\)\footnote{%
  We note that, in general, distributed (decentralized) ledgers cannot 
  withstand a malicious \ac{ISP}.
  Such an adversary can partition the network and provide Alice and Bob with 
  different views of the ledger, thus breaking individual verifiability.
  However, this requires that the adversary \emph{can observe} Alice's and 
  Bob's channels to the ledger --- which is still not true even for 
  \cref{deanonymizing-storage-adversary}.
}.
This means that Alice can check that her proof share is indeed there.

\Cref{UniversalVerif} implies that anyone can check the result and that all 
participation proofs counted are legitimate.
As the proof shares are committed and stored publicly, anyone can
download them, verify eligibility (\ie verify \(\corr_\pid,
\corr_{\wid}\)) of the proofs and count them.
As for individual verifiability, the security of universal verifiability is 
reduced to the properties of the ledger and storage; but universal 
verifiability also depends on the eligibility verification, which we will 
discuss next.

@@

\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
In \CROCUS, we have several attributes that must be verifiable: the time of 
creation (\ie, temporal eligibility, \cref{TemporallyRelated}), the physical 
location of \(\sk_P\) at creation (\ie, spatial eligibility, 
\cref{SpatiallyRelated}), recognition of two proofs originating from the same 
person (\ie, one-proof-per-person eligibility, \cref{CountOnce}) and that the 
proof is indeed designated for the event (\ie, designated-event eligibility, 
\cref{DesignatedEvent}).
It follows from \cref{analysis-individual} that the adversary cannot drop 
submitted proof shares and thus cannot decrease the count.
As indicated in \cref{in-system-adversary,deanonymizing-storage-adversary}, the 
adversary can submit proof shares as everyone else, so the adversary's only 
option is to increase the count.
We will thus let Alice pose as the adversary in this section, as she naturally 
has an incentive to increase the count.

\paragraph{Temporal eligibility}%
\label{analysis-temporal}

@@

\paragraph{Linkability}%
\label{analysis-linkability}

@@

\paragraph{Spatial eligibility}%
\label{analysis-spatial}

\Cref{SpatiallyRelated} is achieved by having a witness vouch anonymously that Alice was indeed on the location when the proof share was created.
To realize this, we must ensure that Alice cannot forge witness signatures.

In the trust-free case (see \cref{ProtocolVerification}), this is realized by 
using the same linkability mechanism as above.
\Ie to forge a witness signature, Alice must produce a \(\wid'\) such that
\begin{multline*}
  \pi_{\wid'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid, \wid', t_s, t_s', l),
\end{multline*}
is accepted by the verifier while not knowing a signature on the secret key 
\(\sk_W'\).
Thus, she must break the \(\AC\) scheme to succeed or get a valid signature on \(\sk_W'\) from the \ac{CA}.
As above, the latter could be done if she can find people willing to collude, 
people unwilling to collude but she can illicitly use their keys anyway or 
simply request new keys from the \ac{CA}.

We assumed that Alice cannot collude with more than a threshold \(\theta\) of 
witnesses.
Thus, setting the threshold of at least \(\theta+1\) will prevent Alice from 
cheating.
(Note that Alice can produce \emph{one} witness signature for herself, since 
she has access to her own \(\sk_P\), but no more.
Thus, \(\theta > 1\) is a requirement in the trust-free case.)

In the trusted witness case, we assume that we can trust (dedicated) witnesses.
In this case, Alice must be able to forge statements, \eg digital signatures, 
from at least one witness that the verifier trusts.

\paragraph{Designated protest}%
\label{analysis-designated}

@@

>>>>

@@

\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
In \CROCUS, we have several attributes that must be verifiable: the time of 
creation (\ie, temporal eligibility, \cref{TemporallyRelated}), the physical 
location of \(\sk_P\) at creation (\ie, spatial eligibility, 
\cref{SpatiallyRelated}), recognition of two proofs originating from the same 
person (\ie, one-proof-per-person eligibility, \cref{CountOnce}) and that the 
proof is indeed designated for the event (\ie, designated-event eligibility, 
\cref{DesignatedEvent}).
As we will show, it follows from \cref{analysis-individual} that the adversary cannot drop 
submitted proof shares and thus cannot decrease the count.
As indicated in \cref{in-system-adversary,deanonymizing-storage-adversary}, the 
adversary can submit proof shares as everyone else, so the adversary's only 
option is to increase the count.
We will thus let Alice pose as the adversary in this section, as she naturally 
has an incentive to increase the count, as the organizer and participant.

\subsubsection{Temporal eligibility}%
\label{analysis-temporal}

@@

\subsubsection{Linkability}%
\label{analysis-linkability}

@@

\subsubsection{Spatial eligibility}%
\label{analysis-spatial}

\Cref{SpatiallyRelated} is achieved by having a witness vouch anonymously that Alice was indeed at the location when the proof share was created.
To realize this, we must ensure that Alice cannot forge witness signatures.

In the trust-free case (see \cref{ProtocolVerification}), this is realized by 
using the same linkability mechanism as above.
\Ie to forge a witness signature, Alice must produce a \(\wid'\) such that
\begin{multline*}
  \pi_{\wid'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid, \wid', t_s, t_s', l),
\end{multline*}
is accepted by the verifier while not knowing a signature on the secret key 
\(\sk_W'\).
Thus, she must break the \(\AC\) scheme to succeed or get a valid signature on \(\sk_W'\) from the \ac{CA}.
As above, the latter could be done if she can find people willing to collude, 
or whose keys she illicitly can use anyway, or 
simply request new keys from the \ac{CA}.

% We assumed that Alice cannot collude with more than a threshold \(\theta\) of 
% witnesses.
% Thus, setting the threshold of at least \(\theta+1\) will prevent Alice from 
% cheating.
% (Note that Alice can produce \emph{one} witness signature for herself, since 
% she has access to her own \(\sk_P\), but no more.
% Thus, \(\theta > 1\) is a requirement in the trust-free case.)

The strength function from ~\cref{DefParticipationCount} ensures that
Alice either has to collude with \(\theta - 1\) witnesses (she can
produce \emph{one} witness signature for herself, since she has access
to her own \(\sk_P\), but no more) or, in the trusted witness case,
that Alice must be able to forge statements, \eg digital signatures,
from at least one witness that the verifier trusts.

\subsubsection{Designated protest}%
\label{analysis-designated}

@@

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
that their participation proofs (\ie proof shares) are indeed included in the 
computed count.
All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger and 
available from a public and permanent storage.
Thus, Alice and Bob can simply check that all of their proof shares are indeed 
there and the security of individual verifiability depends on the properties of 
the ledger and storage (\(\TS\), \cref{timestamp}).
For both \cref{in-system-adversary,deanonymizing-storage-adversary} we assumed 
an honest-but-curious adversary controlling \(\TS\)\footnote{%
  We note that, in general, distributed (decentralized) ledgers cannot 
  withstand a malicious \ac{ISP}.
  Such an adversary can partition the network and provide Alice and Bob with 
  different views of the ledger, thus breaking individual verifiability.
  However, this requires that the adversary \emph{can observe} Alice's and 
  Bob's channels to the ledger --- which is still not true even for 
  \cref{deanonymizing-storage-adversary}.
}.
This means that Alice can check that her proof share is indeed there.

\Cref{UniversalVerif} implies that anyone can check the result and that all 
participation proofs counted are legitimate.
As the proof shares are committed and stored publicly, anyone can
download them, verify eligibility (\ie verify \(\corr_\pid,
\corr_{\wid}\)) of the proofs and count them.
As for individual verifiability, the security of universal verifiability is 
reduced to the properties of the ledger and storage; but universal 
verifiability also depends on the eligibility verification.
